Who does big team science?

### 2023-06-08 manuscript_scopus.Rmd
updating with new data

keywords          : "big team, science, authorship, credit"
wordcount         : "X"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

```{r total-articles}
# updated 
total_num <- 462970
health_num <- 403697
physical_num <- 207192
social_num <- 23020
life_num <- 275249
```

@@

```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
ggplot(DF$pub_time_count %>% 
         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
  ylab("Number of Articles Per Year") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

```{r total-journals}
# updated
journals <- 14263
health_journal <- 6301
physical_journal <- 5505
social_journal <- 2314
life_journal <- 4030
```

@@

```{r tab-snip, results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

@@

# health

health_cloud <- pub_total %>% 
  filter(SubjectArea == "Health Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

physical_cloud <- pub_total %>% 
  filter(SubjectArea == "Physical Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

life_cloud <- pub_total %>% 
  filter(SubjectArea == "Life Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

social_cloud <- pub_total %>% 
  filter(SubjectArea == "Social Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

physical_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Physical Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

life_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Life Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

social_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Social Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r total-authors}
total_authors <- 2786877 # only this updated
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

@@

```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area. Colored dots indicate the mean number of authors, while the black dots represent the median number of authors. The size of the black dots indicate the number of papers in that year."}
avg_author_time <- 
  DF$author_time %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  filter(Number_Papers >= 3) %>% 
  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))

@@

```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
# updated
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.694505, -0.364097, -0.450156, -0.510173)
avg_se_values <- c(0.002903, 0.006058, 0.001443, 0.001924)
sd_b_values <- c(-0.284249, -0.134722, -0.136871, -0.052559)
sd_se_values <- c(0.007381, 0.014757, 0.003646, 0.004821)
r2_values <- c(0.461106, 0.253958, 0.299746, 0.346628)
sample_size <- total_num

@@

```{r total-aff}
# updated
affs <- 434092
```

@@

```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
) %>% 
  filter(publication_type == "ar" | publication_type == "pp" | 
           publication_type == "dp")

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "bottom") + 
  scale_fill_discrete(name = "Publication Type", labels = c("Article", "Data Paper", "Pre-Print"))

@@

```{r}
avg_pub_count_author	<- apa_num(4.451816)
std_pub_count_author <- apa_num(6.901369)

avg_pub_count_paper <- apa_num(7.581413)
sd_pub_count_paper <- apa_num(5.797233)
avg_SD_pub_count_paper <- apa_num(7.140015)
SD_SD_pub_count_paper <- apa_num(5.10383)

avg_HIndex <- apa_num(14.242142)
std_HIndex <- apa_num(43.798203)
med_HIndex <- apa_num(2.0)

avg_of_avg_HIndex <- apa_num(28.136255)
std_of_avg_HIndex <- apa_num(38.013819)
avg_of_std_HIndex <- apa_num(36.430509)
std_of_std_HIndex <- apa_num(46.474619)
med_of_med_HIndex <- apa_num(5.0)
```

@@

```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
# updated 
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(0.005832, -0.026835, -0.020444, -0.007609)
avg_se_values <- c(0.000189, 0.001245, 0.000230, 0.000231)
sd_b_values <- c(-0.023375, 0.015881, 0.008203, -0.003291)
sd_se_values <- c(0.000255, 0.001118, 0.000220, 0.000265)
r2_values <- c(0.137207, 0.033117, 0.046249, 0.030199)
sample_size <- total_num

@@

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
# updated 
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(0.015622, 0.034822, 0.019287, 0.011870)
se_values <- c(0.002748, 0.006295, 0.001209, 0.001552)
r2_values <- c(0.000315, 0.001822, 0.000926, 0.000371)
sample_size <- total_num

>>>>

keywords          : "big team, science, authorship, credit"
wordcount         : "X"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

```{r total-articles}
# updated 
total_num <- 510334
health_num <- 445301
physical_num <- 228194
social_num <- 26652
life_num <- 307514
```

@@

```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
ggplot(DF$pub_time_count %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         filter(Year < 2023), 
       aes(Year, count, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
  ylab("Number of Articles Per Year") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

```{r total-journals}
# updated
journals <- 14924
health_journal <- 6559
physical_journal <- 5787
social_journal <- 2500
life_journal <- 4187
```

@@

```{r tab-snip, results = 'asis', include = TRUE}
# updated
#### make this one table #### 
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r tab-snip-all, results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

@@

# health
health_cloud <- pub_total %>% 
  filter(SubjectArea == "Health Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# physical
physical_cloud <- pub_total %>% 
  filter(SubjectArea == "Physical Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# life
life_cloud <- pub_total %>% 
  filter(SubjectArea == "Life Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# social
social_cloud <- pub_total %>% 
  filter(SubjectArea == "Social Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
# health
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# physical
physical_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Physical Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# life
life_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Life Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

# social 
social_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Social Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r total-authors}
total_authors <- 3047067 # only this updated
#### DAMMIT FORGOT THIS ####
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

@@

```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area. Colored dots indicate the mean number of authors, while the black dots represent the median number of authors. The size of the black dots indicate the number of papers in that year."}
avg_author_time <- 
  DF$author_time %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  # filter(Number_Papers >= 3) %>% 
  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))

@@

```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}

label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
sample_size <- total_num

@@

```{r total-aff}
# updated
affs <- 463876
```

@@

```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
#### try donut chart ####
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")) %>% 
    filter(!is.na(publication_type)) %>% 
  filter(publication_type != "cb")

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "bottom") + 
  scale_fill_discrete(name = "Publication Type")

@@

```{r pub-hindex}
avg_pub_count_author	<- apa_num(38.368910766896065)
std_pub_count_author <- apa_num(102.53740454680472)

avg_pub_count_paper <- apa_num(162.50184385336053)
sd_pub_count_paper <- apa_num(155.1665533053519)
avg_SD_pub_count_paper <- apa_num(164.27249797983876)
SD_SD_pub_count_paper <- apa_num(127.20989934008757)

avg_HIndex <- apa_num(33.64589690529209)
std_HIndex <- apa_num(127.33565834550778)
med_HIndex <- apa_num(8.0)

avg_of_avg_HIndex <- apa_num(198.87318851400775)
std_of_avg_HIndex <- apa_num(248.7847084313958)
avg_of_std_HIndex <- apa_num(211.7985924228093)
std_of_std_HIndex <- apa_num(238.53141146314053)
med_of_med_HIndex <- apa_num(68.0)
```

@@

```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}

label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(0.004248, -0.027315, -0.021713, -0.009466)
avg_se_values <- c(0.000179, 0.001073, 0.000211, 0.000213)
sd_b_values <- c(-0.021552, 0.016810, 0.010139, -0.000378)
sd_se_values <- c(0.000241, 0.000921, 0.000198, 0.000235)
r2_values <- c(0.135965, 0.035968, 0.048999, 0.030748)
sample_size <- total_num

@@

DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ANT"] <- "Western Europe"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BUR"] <- "Western Africa"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"

#### stopped here ####

# BUX-
# BYS -Byelorussian SSR – From June 1992
# CAI-
# CSK-Czechoslovakia – From June 1993
# CZH-
# DDR -East Germany from 1974 to 1990
# EUE  -European Union laissez-passer[6
# HVO -Upper Volta
# PCI -Pacific Islands (Trust Territory)
# ROM- Romania – From February 2002; Code changed to ROU[
# SUN  -USSR From June 2008; Transitionally reserved from September 1992; Officially assigned before being deleted
# SUX-
# TWN- Taiwan still
# UNO-
# YMD -Yemen, Democratic
# YUG -Yugoslavia – From July 2003
# ZAR -Zaire – From July 1997

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}

label <- c("Physical", "Social", "Health", "Life")
b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
sample_size <- total_num
